On exponential sums arising from the classical doubling method

### 2025-04-09 main.tex
alg groups section (missing citation)

\subsubsection{Algebraic groups}
\elad{Tell the reader that the notation $\algebraicGroup{G}$ refers to an algebraic group, which can be thought of as the $\algebraicClosure{\finiteField}$ points of a variety over $\finiteField$ with an action of $\Frobenius$}

>>>>

\subsubsection{Algebraic groups over finite fields}
\elad{Tell the reader that the notation $\algebraicGroup{G}$ refers to an algebraic group, which can be thought of as the $\algebraicClosure{\finiteField}$ points of a variety over $\finiteField$ with an action of $\Frobenius$}
Each of our classical groups $G$ in the proceeding sections are defined by polynomial equations in entries in a matrix which yield an \emph{algebraic group}-an algebraic variety with a group structure (see cite something). 
We will denote the algebraic group by the bold $\algebraicGroup{G}$. 
It can be thought of as its $\algebraicClosure{\finiteField}$ points together with an action of $\Frobenius$ on these points whose fixed points is $\algebraicGroup{G}(\finiteField)$. 
Thus we will often denote $\algebraicGroup{G}(\finiteField)$ by $\algebraicGroup{G}^{\Frobenius}$ or just by the non-bold $G$.
